### 2020-03-09 Common/chapters/deep_learning.tex
Julien and Johan: minors

\subsection{Weight initialization}
\label{weight_initialization}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}Before training a neural network, the weights have to be initialized in order to proceed to the first forward propagation. The initialization of the neural network weights is crucial since it will determine how quickly the network converges to an optimum. The idea behind weight initialization is to generate an initialization that "prevents layer activation outputs from exploding or vanishing during the course of a forward pass through a deep neural network. If either occurs, loss gradients will either be too large or too small to flow backwards beneficially, and the network will take longer to converge, if it is even able to do so at all"~\cite{27}.

@@

\noindent The output of the entire convolution shows negative values in the outside parts and large positive values in the center. This means that the $3x3$ filter detected a vertical line in the center of the input image.

@@

\section{Transfer learning}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}According to Jason Brownlee, "transfer learning is a machine learning method where a model developed for a task is reused as the starting point for a model on a second task"~\cite{30}. The model dedicated to the second task uses some or all parts of the first model (i.e. keeps the same weights and architecture or a part of them) and is then retrained on data available for this task. The first model can either be implemented from scratch if enough data is available or it can simply be downloaded from institutions that release large pretrained models for similar tasks. There are three major benefits~\cite{30}:
\begin{itemize}
\item Higher start: The initial skill (before refining the model) on the source model is higher than it otherwise would be.
\item Higher slope: The rate of skill improvement during training of the source model is steeper than it otherwise would be.
\item Higher asymptote: The converged skill of the trained model is better than it otherwise would be.
\end{itemize}
Nevertheless, "in general, it is not obvious that there will be a benefit to using transfer learning in the domain until after the model has been developed and evaluated"~\cite{30}.

>>>>

\subsection{Weight initialization}
\label{weight_initialization}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}Before training a neural network, the weights have to be initialized in order to proceed to the first forward propagation. The initialization of the neural network weights is crucial since it will determine how quickly the network converges to an optimum. According to James Dellinger, the idea behind weight initialization is to generate an initialization that "prevents layer activation outputs from exploding or vanishing during the course of a forward pass through a deep neural network. If either occurs, loss gradients will either be too large or too small to flow backwards beneficially, and the network will take longer to converge, if it is even able to do so at all"~\cite{27}.

@@

\noindent The output of the entire convolution shows negative values in the outside parts and large positive values in the center. This means that the $3x3$ filter detected a vertical line in the center of the input image. Like other parameters, filters are learned while training.

@@

\section{Transfer learning}
\setlength{\marginparwidth}{3cm}\leavevmode \marginnote{\textbf{Jobin}}According to Jason Brownlee, "transfer learning is a machine learning method where a model developed for a task is reused as the starting point for a model on a second task"~\cite{30}. The model dedicated to the second task uses some or all parts of the first model (i.e. keeps the same weights and architecture or a part of them) and is then retrained on data available for this task. The first model can either be implemented from scratch if enough data is available or downloaded from institutions that release large pretrained models for similar tasks. Transfer learning provides three major benefits~\cite{30}:
\begin{itemize}
\item Higher start: The initial skill (before refining the model) on the source model is higher than it otherwise would be.
\item Higher slope: The rate of skill improvement during training of the source model is steeper than it otherwise would be.
\item Higher asymptote: The converged skill of the trained model is better than it otherwise would be.
\end{itemize}
Nevertheless, "in general, it is not obvious that there will be a benefit to using transfer learning in the domain until after the model has been developed and evaluated"~\cite{30}.
